A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-10 4_method.tex
rewrite significance measure section

\subsection{Beading}
We assign a beading to each significant node (and each local optimum).

\subsubsection{Significance measure}\label{sec:significance_measure}
\Cref{rounded_dist_measures}
We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
Equivalently we can look at the \emph{bisector angle} $\alpha$ between a skeletal point and the two closest points on the outline.
(Same definition as \cite{attali1996modeling}.)

Contrary to common techniques we will \emph{keep} the insignificant regions of the skeleton.

\paragraph{line-line bones}
When the angle between two outline segments is small, the naive method will produce long triangular gaps.
A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between $R$ and Euclidean distance.
Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.
See \cref{distance_based_angles}.

@@

\paragraph{line-point segments}
For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
If $\alpha > \SI{120}{\degree}$ then $\tan^{-1} \abs \partial y / \partial x < \SI{30}{\degree}$,
i.e.  $\tan^{-1} \abs x/d < \SI{30}{\degree}$,
i.e. when $\abs x/d < 1 / \sqrt{3}$,
i.e. when $\abs x < d \sqrt{3} / 3$.
So we mark the part of the parabola as to-be-transformed for which $x \in [-d \sqrt{3} / 3, d \sqrt{3} / 3]$.
See \cref{end_of_markings_point_point}.

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/end_of_markings_point_line.pdf}
\caption{End-of-markings for a parabolic spine segment.}
\label{end_of_markings_point_point}
\end{figure}

\paragraph{point-point bones}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the angle $\alpha > \SI{120}{\degree}$ when $\abs(x) < \frac12 d \tan \SI{30}{\degree} $,
so we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-d \sqrt{3}/6, d \sqrt{3}/6]$.
See \cref{end_of_markings_point_point}.

\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/end_of_markings_point_point.pdf}
\caption{End-of-markings for the segment(s) generated by two outline verts.}
\label{end_of_markings_point_point}
\end{figure}

\paragraph{MAT distance transform}
In order to apply the beading strategy to the MAT
we assign each node $v$ of the medial axis a bead quantity $B^*$ which is initially based on $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.

\hl{How should we define $B^*$? Currently it is always the rounded measure, but it needs to be unrounded in non-marked areas and it needs to support fractional numbers around transitions!}

The bead quantity measure $B^*$ measure should be rounded
where the MAT distance measure $R$ is a local maximum: when all directly connected nodes have a lower MAT distance measure.
See bottom of \cref{rounded_vs_unrounded}.

>>>>

\subsection{Beading}
We assign a bead count to each node in the skeleton which is connected to a bone which is in `the center' of the shape
and also to each node with locally optimal feature radius $R$.
Around regions where the bead count changes we introduce transition regions.

\subsubsection{Significance measure}\label{sec:significance_measure}
\Cref{rounded_dist_measures}
Places where the naive concentric toolpathing strategy would create large underfilling and overfilling areas are locations which intuitively look like `the center' of the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\widehat{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill.
Contrary to related literature we will \emph{keep} the insignificant regions of the skeleton.
Our framework will employ a different toolpathing strategy to prevent overfill and underfill areas if they would be so large that $\alpha > \alpha_\text{max}$.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{sources/method/naive_overfill_underfill.pdf}
\caption{
Overfill and underfill areas in a naive beading using a constant bead witdh $w$ of a wedge area with vertex angle $\beta$.
The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
}
\label{naive_overfill_underfill}
\end{figure}

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance.
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \sin(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This ratio can be immediately applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex and another vertex or line segment, we could exactly determine at which location $\frac{\partial R}{\partial x} > \sin(\alpha_\text{max} / 2)$.
However, because we have discretized such segments, we can approximate the location by applying our ratio based significance measure on the piecewise linear approximating segments directly.

@@

Any node in the skeleton can have at most two significant bones connected to it, because we have limited $\alpha_\text{max} > 120\degree$,
while the corners of a triangle can only add up to \SI{180}{\degree}.
\todo{TODO: make figure which clearly shows this!}
This results in the fact that we will never have 3-way intersections of non-closed extrusion toolpaths.

\paragraph{Bead counts}
In order to apply the beading strategy to the VQ
we assign each significant node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.

We also assign a bead count $v.B^*=b(R(v))$ to all nodes $v$ which are local maxima, i.e. the $v$ for which $\forall v_\text{n} \in v.\text{neighborhood} : R(v) > R(v_\text{n})$. 
This prevents the single overfill or underfill region in non-significant regions.
See \cref{rounded_vs_unrounded}.
